\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.5in, landscape]{geometry}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{xcolor}

\begin{document}

\begin{center}
    \Huge\textbf{User Traffic Analysis \& Scaling Phases}
\end{center}

\vspace{0.5cm}

\renewcommand{\arraystretch}{1.5}
\noindent
\begin{tabularx}{\textwidth}{@{} 
    >{\hsize=0.8\hsize\raggedright\arraybackslash}X 
    >{\hsize=0.6\hsize\raggedright\arraybackslash}X 
    >{\hsize=0.8\hsize\raggedright\arraybackslash}X 
    >{\hsize=1.6\hsize\raggedright\arraybackslash}X 
    >{\hsize=1.6\hsize\raggedright\arraybackslash}X 
    >{\hsize=0.6\hsize\raggedright\arraybackslash}X @{}}
\toprule
\textbf{Phase} & \textbf{Active Users (DAU \& MAU)} & \textbf{Peak Concurrent (CCU) \& Video} & \textbf{Infrastructure \& Plans Required} & \textbf{System Status \& Notes} & \textbf{Est. Cost/Mo} \\
\midrule
\textbf{Phase 1: Free Tier} \newline \textit{Beta \& Early Launch} 
& \textbf{DAU:} 0 -- 1,000 \newline \textbf{MAU:} 0 -- 30,000
& \textbf{CCU:} Up to 100 \newline \textbf{Video:} 50+ calls \newline \textbf{New:} $<$ 50/day
& \textbf{Backend:} Render Free Tier (512MB RAM) \newline \textbf{Database:} MongoDB M0 (Max 500 connections) \newline \textbf{Resend:} Free Tier (100 emails/day)
& \textcolor{green!70!black}{\textbf{Highly Capable:}} Node.js handles 100s of WebSockets easily. WebRTC video is Peer-to-Peer, requiring ZERO backend bandwidth.
& \$0 \\
\midrule
\textbf{Phase 2: Standard Tier} \newline \textit{Growth \& Marketing}
& \textbf{DAU:} 1,000 -- 10,000 \newline \textbf{MAU:} 30,000 -- 300,000
& \textbf{CCU:} 100 -- 1,000 \newline \textbf{Video:} 500+ calls \newline \textbf{New:} 100 -- 500/day
& \textbf{Backend:} Render Standard (\$25) - 2GB RAM \newline \textbf{Database:} MongoDB M10 (\$25) - Higher connection limits \newline \textbf{Resend:} Pro Tier (\$20)
& \textcolor{green!70!black}{\textbf{Perfectly Stable:}} A single Node.js instance on 2GB RAM can hold over 10,000 concurrent socket connections effortlessly.
& \$70 \\
\midrule
\textbf{Phase 3: High Density} \newline \textit{Established Brand}
& \textbf{DAU:} 10,000 -- 50,000 \newline \textbf{MAU:} 300,000 -- 1.5M
& \textbf{CCU:} 1,000 -- 5,000 \newline \textbf{Video:} 2,000+ calls \newline \textbf{New:} 1,000+/day
& \textbf{Backend:} Render Pro (\$50) - 4GB RAM, 2 CPUs \newline \textbf{Database:} MongoDB M20 (\$60) \newline \textbf{Resend:} Pro Tier (\$30)
& \textcolor{orange!90!black}{\textbf{Approaching CPU Limit:}} The memory (4GB) is plenty, but the single-threaded Node.js event loop will start getting saturated at 5,000+ highly active CCU.
& \$140 \\
\midrule
\textbf{Phase 4: Multi-Instance Scale} \newline \textit{Enterprise Traffic}
& \textbf{DAU:} 50,000 -- 250,000+ \newline \textbf{MAU:} 1.5M -- 7.5M+
& \textbf{CCU:} 5,000 -- 30,000+ \newline \textbf{Video:} 10,000+ calls
& \textbf{Backend:} AWS EC2 Auto-Scaling or Render Load Balancing (\$150+) \newline \textbf{Database:} Dedicated M40+ Cluster (\$300+) \newline \textbf{Redis:} Managed Redis (\$15)
& \textcolor{blue!80!black}{\textbf{Infinite Horizontal Scale:}} Requires integrating a Redis Adapter to sync Socket.io events across multiple NodeJS server instances.
& \$500+ \\
\bottomrule
\end{tabularx}

\vspace{1cm}
\noindent\Large\textbf{Why Your Code is Incredibly Scalable} \normalsize \\
\vspace{0.2cm} \\
Your current codebase leverages \textbf{Node.js}, which is highly optimized for asynchronous I/O and WebSocket handling. Because your backend relies on \textbf{raw WebRTC} for video calls, the server only acts as a signaling mechanism. Once the initial handshake (offer/answer) is complete, the video stream is \textbf{Peer-to-Peer}, meaning it consumes 0\% CPU and 0\% bandwidth on your server. 
\newline\newline
A single \$25 Render instance (2GB RAM) allocates roughly 50KB per socket connection, allowing you to comfortably hold \textbf{over 10,000 concurrent users} before hitting memory limits. You only need to scale to Multi-Instance (Phase 4) when the single-threaded CPU event loop becomes the bottleneck, typically around 5,000+ highly active concurrent connections doing constant chat operations.

\end{document}
